Lyman-alpha spectra from rotating outflows

### 2017-11-14 paper/paper.tex
some edits in the itro

Currently LAEs are commonly targeted in wide area galaxy surveys.
They have been effectively used to study galaxy evolution,
cosmology and the thermal history of the Universe.
This has been possible through the study of their spatial distribution and
the shape of their \lya emission line.

@@

One of the ISM's features that plays an important role in shaping the \lya
is \HI kinematics. 
In a static \HI medium the \lya line ha  two equal and symmetric peaks
around the natural \lya wavelength and zero intensity at the line's
center.
For an outflowing ISM, the line becomes
asymmetrical with a more pronounced read peak.
If the galaxy rotates, the line shows different amounts of Doppler
shifts modifying the overall line profile \citep{Garavito14}.

In this paper we present for the first time a study of the joint
effects of galaxy outflows and rotation.
We study a simplified geometrical configuration corresponding to a
spherical gas cloud with symmetrical radial outflows and a rotation
profile corresponding to a solid body.
We base our modeling on a Monte-Carlo radiative transfer code called
CLARA (Code for Lyman Alpha Radiation Analysis) presented for the
first time by \cite{CLARA}.
Besides modeling the impact of joint rotation and outflows, we also
want to check to what extent the analytical model presented by
\cite{Garavito14} to explain the effects of rotation can also be
applied in our case.

In this paper we introduce first our theoretical tools and assumptions
in Section \ref{sec:theory}. We continue in Section  \ref{sec:results}
with the results from the Monte-Carlo simulation, the comparison
against the semi-analytical approximation which we use to make a
thorough exploration of the effect of rotation.
In Section \ref{sec:discussion} we discuss our results and their
possible implications for observational analysis to finally present
our conclusions in Section \ref{sec:conclusions}.

>>>>

Currently LAEs are commonly targeted in wide area galaxy surveys.
The conditions that allow for the emergence of the lYa line is that
these galaxies are star forming with a low dust content. 
They have been effectively used to study galaxy evolution,
cosmology and the thermal history of the Universe.
This has been possible through the study of their spatial distribution and
the shape of their \lya emission line.

@@

These kinematic maps show that lyman alpha emitting galaxies have two 
overimposed velocity patterns: coherent rotation plus and a random
motions around the mean value provided by rotation. 
Depending on the system under study, one of the two features can be
more important, or they can be found in equal measure. 
These kinematic features play an important role in shaping the \lya.

Models of the \lya have also shown that there is clear signal for
outflowing gas most probably produced by star formation activity.
The characteristic signal for these outflows is the asymmetrical \lya
linea with a more pronounced read peak.

The effects of either outflows or rotation on the \lya line have been
already explored.
Here e present for the first time a study of the joint effects of
galaxy outflows and rotation, two of the three major kinematic
components expected in LAEs.

We study a simplified geometrical configuration corresponding to a
spherical gas cloud with symmetrical radial outflows and a rotation
profile corresponding to a solid body.
We base our modeling on a Monte-Carlo radiative transfer code called
CLARA (Code for Lyman Alpha Radiation Analysis) presented for the
first time by \cite{CLARA}.

Besides modeling the impact of joint rotation and outflows, we also
check to what extent the analytical model presented by
\cite{Garavito14} to explain the effects of rotation can also be
applied in our case.
We show that solid body rotation effects can be included
in the results of other radiative transfer model in the case of large
optical depths. In this case it is a good approximation to Doppler
boost the results of the model without rotation.

The structure of the paper is the following. 
We introduce first our theoretical tools and assumptions
in Section \ref{sec:theory}. We continue in Section  \ref{sec:results}
with the results from the Monte-Carlo simulation, the comparison
against the semi-analytical approximation which we use to make a
thorough exploration of the effect of rotation.
In Section \ref{sec:discussion} we discuss our results and their
possible implications for observational analysis to finally present
our conclusions in Section \ref{sec:conclusions}.
